Resurgence of the Airy function \\ and other exponential integrals

### 2022-08-19 exp-resurgence.tex
Move into outline into section

\item The series $\tilde{\phi}$ turns out to have a positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$. By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.

@@

\item \textbf{A new dictionary for ODEs.} The Laplace transform is often usd to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain. We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain. This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.

@@

\item Some have been discussed many times, using different approaches and conventions. We'll try to give an idea of how all these different treatments fit together. $\bullet$ The Airy function. $\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).

@@

\item \textcolor{magenta}{To understand, for example, the Ecalle formalism, you can start with these toy examples, which illustrate what's going on, but can also be studied in a more elementary way. [How do we work this into the introduction?]}

@@

>>>>

@@

@@

@@

@@

%%\end{itemize}
